---
title: CompReproducibility
authors:
  - name: Alex
    affiliation: KU Leuven
    roles: writing
    corresponding: true
bibliography: references.bib
csl: apa.csl
---

```{r results="hide"}
source("./load_environment.R")
```

## Introduction

Metacognition important, bla bla bla.<br>
@Carpenter_etal_2019 tried to show that they could improve metacognitive _monitoring_ but their positive results seems to be mostly explained by experimental confounds [@Rouy_etal_2022 ; @Soto_etal_2024]. @Haddara_Rahnev_2022 showed tho that it is difficult with type-I feedback.

## Methods

We collected `r unique(df$id)` participants, splitted in a training group and a control group.
<!-- Kobe: indicate the informed consent --> 

## Results

```{r}
test <- lm(value ~ group, data = df)
```

There is a significant effect of the training on metacognitive monitoring `r lm_output(test, "grouptraining")`, with the metacognitive training group having a higher average `r value_output(mean(df$value[df$group == "training"]), sd(df$value[df$group == "training"]))` than the control group `r value_output(mean(df$value[df$group == "non_training"]), sd(df$value[df$group == "non_training"]))` (see @fig-plotDiff). The metacognitive monitoring score was based on the M-ratio (@eq-mratio), which is the ratio of meta-d' to d', where meta-d' is a measure of metacognitive sensitivity and d' is a measure of task performance:
$$
M-ratio = \frac{meta-d'}{d'}
$$ {#eq-mratio}

```{r}
#| label: fig-plotDiff
#| fig.cap: "Metacognitive monitoring scores by group"
ggplot(df, aes(x = group, y = value)) +
  geom_boxplot() +
  geom_jitter(width = 0.2) +
  labs(x = "Group",
       y = "Metacognitive monitoring score") +
  theme_minimal()
```

